The problem and promise of scale in multilayer networks

### 2020-01-23 paper/manuscript.Rmd
edit fitness Paragraph1

Social network positions are frequently used to represent the social environment that an individual experiences or their social phenotype, and they are increasingly linked to important fitness outcomes for individuals among species ranging from primates (e.g. Brent, Ruiz-Lambides, & Platt, 2017; Thompson, 2019) to dolphins (e.g. Stanton & Mann, 2012; Stanton, Gibson, & Mann, 2011) to birds (e.g. McDonald, 2007; Royle, Pike, Heeb, Richner, & Kolliker, 2012). But there are many ways that scale comes into play in determining how characteristics of an individual’s social network position are related to fitness that depend on the hypotheses being tested and logistical constraints. The two scales that repeatedly come across as important for understanding fitness consequences are temporal and social scale (Almeling, Hammerschmidt, Sennhenn-Reulen, Freund, & Fischer, 2016; Berger, Lemaître, Allainé, Gaillard, & Cohas, 2015; Brent et al., 2017).

>>>>

Social network positions are frequently used to represent the social environment that an individual experiences or their social phenotype. Social phenotypes are increasingly linked to important fitness for individuals of various species, including primates (e.g. Brent, Ruiz-Lambides, & Platt, 2017; Thompson, 2019), dolphins (e.g. Stanton & Mann, 2012; Stanton, Gibson, & Mann, 2011), and birds (e.g. McDonald, 2007; Royle, Pike, Heeb, Richner, & Kolliker, 2012). The effect of scale on the relationship between an individual’s social network position and fitness may depend on the hypotheses being tested and logistical constraints. Two scales that are important for understanding fitness consequences in the context of social network positions are temporal and social scales (Almeling, Hammerschmidt, Sennhenn-Reulen, Freund, & Fischer, 2016; Berger, Lemaître, Allainé, Gaillard, & Cohas, 2015; Brent et al., 2017).
